\documentclass[a4paper,10pt]{article}
\usepackage[utf8]{inputenc}
\usepackage[left=1in,right=1in,top=1in,bottom=1in]{geometry}
\usepackage{enumitem}
\usepackage{hyperref}

\setlength\parindent{0pt}

\makeatletter
\renewcommand\maketitle{
    \begin{flushleft}
        \huge\textbf{\@title}
    \end{flushleft}
}
\makeatother

\begin{document}

\title{Abhishek Kapoor - iOS Developer Resume}
\date{}
\maketitle

\section*{Contact}
\begin{itemize}
    \item Phone: +91 77427 55223
    \item Email: \href{mailto:abhikapoor2000.ak@gmail.com}{abhikapoor2000.ak@gmail.com}
    \item LinkedIn: \href{https://www.linkedin.com/in/abhishekkapoorfullstack/}{LinkedIn Profile}
\end{itemize}

\section*{Summary}
Dedicated iOS developer with expertise in Swift, Flutter, and UI design, known for enhancing user experiences and cost efficiency.

\section*{Skills}
Swift, Dart, Java, C, C++, XCode, Android Studio, UI-Kit, Swift UI, Flutter, Core data, Spring boot, Data Structures, Databases.

\section*{Experience}

\subsection*{Fi Money - iOS Developer (2023 - Present)}
\begin{itemize}
    \item Managed Finvu Account Aggregate SDK, boosting monthly balances.
    \item Spearheaded integration of fund transfer features, improving iOS user balance.
    \item Set up unit testing for better code quality and issue detection.
\end{itemize}

\subsection*{Parkplus - iOS Developer (2022)}
\begin{itemize}
    \item Developed B2C iOS apps with 99% crash-free user experience.
    \item Integrated progressive web app (PWA) for enhanced user experience.
    \item Implemented Payments using juspay for hassle-free transactions.
\end{itemize}

\subsection*{Blueberry Fun - iOS Developer (2021)}
\begin{itemize}
    \item Designed apps for kids, using UI-kit and MVVM pattern.
    \item Completed fleet management app for tracking drivers using Flutter.
    \item Implemented new tech stack in the mobile team.
\end{itemize}

\section*{Education}
Bachelor of Engineering in Computer Science, Arya College of Engineering and Research Centre (2017 - 2021), CGPA: 7.6/10.0

\section*{Achievements}
Winner of CodeNRun Hackathon, 5 stars in Java and C++ on Hackerrank, TCS Code vita ranks AIR 600, College ranks 1st at Geeksforgeeks.

\section*{Personal Project: Blind-75}
\begin{itemize}
    \item Comprehensive collection of 75 data structure and algorithm questions with explanations and solutions.
\end{itemize}

\end{document}
